### 2023-05-31 paper/paper.tex
Add paper latex documents

% Paper template for TAR 2022
% (C) 2014 Jan Šnajder, Goran Glavaš, Domagoj Alagić, Mladen Karan
% TakeLab, FER

\documentclass[10pt, a4paper]{article}

\usepackage{tar2023}

\usepackage[utf8]{inputenc}
\usepackage[pdftex]{graphicx}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{amssymb}

\title{TAR System Description Paper Template}

\name{Author1, Author2, Author3}

\address{
University of Zagreb, Faculty of Electrical Engineering and Computing\\
Unska 3, 10000 Zagreb, Croatia\\ 
\texttt{autor1@xxx.hr}, \texttt{\{autor2,autor3\}@zz.com}\\
}

\abstract{ 
This document provides the instructions on formatting the TAR system description paper in \LaTeX{}. This is where you write the abstract (i.e., summary) of the work you carried out within the project. The abstract is a paragraph of text ranging between 70 and 150 words.
}

\begin{document}

\maketitleabstract

\section{Introduction}

This section is the introduction to your paper.
Introduction should not be too elaborate, as that is what other sections are for (the Introduction should definitely not spill over to the second page).

This is the second paragraph of the introduction.
In \LaTeX , paragraphs are separated by inserting an empty line in between them.
Avoid very large paragraphs (larger than half of the page height), but also avoid tiny paragraphs (e.g., one-sentence paragraphs)

\section{Second section}

In scientific papers, this section usually (but not necessarily) briefly describes the related research and what makes the presented approach different from it.

\subsection{First subsection}
\label{sec:first}

This is a subsection of the second section.

\subsection{Second subsection}

This is the second subsection of the second section.
Referencing the (sub)sections in text is performed as follows: ``in Section~\ref{sec:first} we have shown \dots''.

\subsubsection{Sub-subsection example}

This is a sub-subsection.
If possible, it is better to avoid sub-subsections.

\section{Extent of the paper}

The paper should have a minimum of 3 and a maximum of 4 pages, plus an additional page for references.

\section{Figures and tables}

\subsection{Figures}

Here is an example on how to include figures in the paper.
Figures are included in \LaTeX{} code immediately \textit{after} the text in which these figures are referenced.
Allow \LaTeX{} to place the figure where it believes is best (usually on top of the page of at the position where you would not place the figure).
Figures are referenced as follows: ``Figure~\ref{fig:figure1} shows \dots''.
Use tilde (\verb.~.) to prevent separation between the word ``Figure'' and its enumeration.

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figures/drawing}
\caption{This is the figure caption. Full sentences should be followed with a dot. The caption should be placed \textit{below} the figure. Caption should be short; details should be explained in the text.}
\label{fig:figure1}
\end{center}
\end{figure}

\subsection{Tables}

There are two types of tables: narrow tables that fit into one column and a wide table that spreads over both columns.

\subsubsection{Narrow tables}

Table~\ref{tab:narrow-table} is an example of a narrow table.
Do not use vertical lines in tables -- vertical tables have no effect and they make tables visually less attractive.
We recommend using \textit{booktabs} package for nicer tables.

\begin{table}
\caption{This is the caption of the table. Table captions should be placed \textit{above} the table.}
\label{tab:narrow-table}
\begin{center}
\begin{tabular}{ll}
\toprule
Heading1 & Heading2 \\
\midrule
One & First row text \\
Two   & Second row text \\
Three   & Third row text \\
      & Fourth row text \\
\bottomrule
\end{tabular}
\end{center}
\end{table}

\subsection{Wide tables}

Table~\ref{tab:wide-table} is an example of a wide table that spreads across both columns.
The same can be done for wide figures that should spread across the whole width of the page.

\begin{table*}
\caption{Wide-table caption}
\label{tab:wide-table}
\begin{center}
\begin{tabular}{llr}
\toprule
Heading1 & Heading2 & Heading3\\
\midrule
A & A very long text, longer that the width of a single column & $128$\\
B & A very long text, longer that the width of a single column & $3123$\\
C & A very long text, longer that the width of a single column & $-32$\\
\bottomrule
\end{tabular}
\end{center}
\end{table*}

\section{Math expressions and formulas}

Math expressions and formulas that appear within the sentence should be written inside the so-called \emph{inline} math environment: $2+3$, $\sqrt{16}$, $h(x)=\mathbf{1}(\theta_1 x_1 + \theta_0>0)$.
Larger expressions and formulas (e.g., equations) should be written in the so-called \emph{displayed} math environment:

\[
b^{(i)}_k = \begin{cases}
1 & \text{if 
    $k = \text{argmin}_j \| \mathbf{x}^{(i)} - \mathbf{\mu}_j \|,$}\\
0 & \text{otherwise}
\end{cases}
\]

Math expressions which you reference in the text should be written inside the \textit{equation} environment:

\begin{equation}\label{eq:kmeans-error}
J = \sum_{i=1}^N \sum_{k=1}^K 
b^{(i)}_k \| \mathbf{x}^{(i)} - \mathbf{\mu}_k \|^2
\end{equation}

Now you can reference equation \eqref{eq:kmeans-error}.
If the paragraph continues right after the formula

\begin{equation}
f(x) = x^2 + \varepsilon
\end{equation}

\noindent like this one does, use the command \emph{noindent} after the equation to remove the indentation of the row.

Multi-letter words in the math environment should be written inside the command \emph{mathit}, otherwise \LaTeX{} will insert spacing between the letters to denote the multiplication of values denoted by symbols.
For example, compare
$\mathit{Consistent}(h,\mathcal{D})$ and\\
$Consistent(h,\mathcal{D})$.

If you need a math symbol, but you don't know the corresponding \LaTeX{} command that generates it, try
\emph{Detexify}.\footnote{\texttt{http://detexify.kirelabs.org/}}

\section{Referencing literature}

References to other publications should be written in brackets with the last name of the first author and the year of publication, e.g., \citep{chomsky-73}.
Multiple references are written in sequence, one after another, separated by semicolon and without whitespaces in between, e.g., \citep{chomsky-73,chave-64,feigl-58}.
References are typically written at the end of the sentence and necessarily before the sentence punctuation.

If the publication is authored by more than one author, only the name of the first author is written, after which abbreviation \emph{et al.}, meaning \emph{et alia}, i.e.,~and others is written as in \citep{johnson-etc}.
If the publication is authored by only two authors, then the last names of both authors are written \citep{johnson-howells}.

If the name of the author is incorporated into the text of the sentence, it should not be in the brackets (only the year should be there).
E.g.,~``\citet{chomsky-73} suggested that \dots''.
The difference is whether you reference the publication or the author who wrote it.

The list of all literature references is given alphabetically at the end of the paper.
The form of the reference depends on the type of the bibliographic unit: conference papers~\citep{chave-64}, books~\citep{butcher-81}, journal articles~\citep{howells-51}, doctoral dissertations~\citep{croft-78}, and book chapters~\citep{feigl-58}.

All of this is automatically produced when using BibTeX. Insert all the BibTeX entries into the file \texttt{tar2023.bib}, and then reference them via their symbolic names.

\section{Conclusion}

Conclusion is the last enumerated section of the paper.
It should not exceed half of a column and is typically split into 2--3 paragraphs.
No new information should be presented in the conclusion;
this section only summarizes and concludes the paper.

\section*{Acknowledgements}

If suitable, you can include the \textit{Acknowledgements} section before inserting the literature references  in order to thank those who helped you in any way to deliver the paper, but are not co-authors of the paper.

\bibliographystyle{tar2023}
\bibliography{tar2023}

\end{document}

### 2023-05-31 paper/compile.py

@@ -1,0 +1,40 @@
+import os
+import subprocess
+import sys
+
+
+def init_folder(folder_name):
+    if not os.path.isdir(folder_name):
+        os.mkdir(folder_name)
+
+
+if __name__ == '__main__':
+    if len(sys.argv) > 1 and sys.argv[1] in ['-h', '--help', '-help', '-?']:
+        print('''
+        python compile.py [ tex_file_name ]
+        
+        Starting this program without any arguments will search for the .tex file with the same name as the parent folder.
+        If a parameter is given, the program will search for the .tex file with the name [parameter].tex.
+        ''')
+        exit(0)
+
+    file_name = os.path.split(os.getcwd())[1]
+    if len(sys.argv) > 1:
+        file_name = sys.argv[1]
+
+    if not os.path.isfile(f"{file_name}.tex"):
+        print(f"There is no file with name '{file_name}.tex'")
+        exit(1)
+
+    auxiliary_dir = 'auxiliary'
+    init_folder(auxiliary_dir)
+
+    commands = [
+        ['pdflatex', f'-aux-directory={auxiliary_dir}', f'{file_name}.tex'],
+        ['bibtex', f'{auxiliary_dir}/{file_name}.aux'],
+        ['pdflatex', f'-aux-directory={auxiliary_dir}', f'{file_name}.tex'],
+        ['pdflatex', f'-aux-directory={auxiliary_dir}', f'{file_name}.tex'],
+    ]
+
+    for c in commands:
+        subprocess.call(c)

### 2023-05-31 paper/paper.tex
Initialize main latex file and cleanup paper directory

@@
 
-\title{TAR System Description Paper Template}
+\title{Stress Analysis in Social Media}
 
-\name{Author1, Author2, Author3}
+\name{Sven Šćekić, Marko Kuzmić, Lovro Bučar}
 
@@
     Unska 3, 10000 Zagreb, Croatia\\
-\texttt{autor1@xxx.hr}, \texttt{\{autor2,autor3\}@zz.com}\\
+    \texttt{\{sven.scekic, marko.kuzmic, lovro.bucar\}@fer.hr}\\
 }
@@
 \abstract{
-This document provides the instructions on formatting the TAR system description paper in \LaTeX{}.
-This is where you write the abstract (i.e., summary) of the work you carried out within the project.
+    Here we can write an abstract of the paper.
     The abstract is a paragraph of text ranging between 70 and 150 words.
@@
 This section is the introduction to your paper.
-Introduction should not be too elaborate, as that is what other sections are for (the Introduction should definitely not spill over to the second page).
 
-This is the second paragraph of the introduction.
-In \LaTeX , paragraphs are separated by inserting an empty line in between them.
-Avoid very large paragraphs (larger than half of the page height), but also avoid tiny paragraphs (e.g., one-sentence paragraphs)
-
-\section{Second section}
+\section{Related Work}
 
 In scientific papers, this section usually (but not necessarily) briefly describes the related research and what makes the presented approach different from it.
+Demonstration of citing~\citep{maguire-76}.
 
-\subsection{First subsection}
-\label{sec:first}
+\section{Dataset}
 
-This is a subsection of the second section.
+A section that will be used to describe the dataset that was used in the research paper.
 
-\subsection{Second subsection}
+\section{Baseline Models}
 
-This is the second subsection of the second section.
-Referencing the (sub)sections in text is performed as follows: ``in Section~\ref{sec:first} we have shown \dots''.
+This section which will describe the models that were used to determine the
 
-\subsubsection{Sub-subsection example}
+\section{Results}
 
-This is a sub-subsection.
-If possible, it is better to avoid sub-subsections.
-
-\section{Extent of the paper}
-
-The paper should have a minimum of 3 and a maximum of 4 pages, plus an additional page for references.
-
-\section{Figures and tables}
-
-\subsection{Figures}
-
-Here is an example on how to include figures in the paper.
-Figures are included in \LaTeX{} code immediately \textit{after} the text in which these figures are referenced.
-Allow \LaTeX{} to place the figure where it believes is best (usually on top of the page of at the position where you would not place the figure).
-Figures are referenced as follows: ``Figure~\ref{fig:figure1} shows \dots''.
-Use tilde (\verb.~.) to prevent separation between the word ``Figure'' and its enumeration.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=\columnwidth]{figures/drawing}
-\caption{This is the figure caption.
-Full sentences should be followed with a dot.
-The caption should be placed \textit{below} the figure.
-Caption should be short; details should be explained in the text.}
-\label{fig:figure1}
-\end{center}
-\end{figure}
-
-\subsection{Tables}
-
-There are two types of tables: narrow tables that fit into one column and a wide table that spreads over both columns.
-
-\subsubsection{Narrow tables}
-
-Table~\ref{tab:narrow-table} is an example of a narrow table.
-Do not use vertical lines in tables -- vertical tables have no effect and they make tables visually less attractive.
-We recommend using \textit{booktabs} package for nicer tables.
-
-\begin{table}
-\caption{This is the caption of the table. Table captions should be placed \textit{above} the table.}
-\label{tab:narrow-table}
-\begin{center}
-\begin{tabular}{ll}
-\toprule
-Heading1 & Heading2 \\
-\midrule
-One & First row text \\
-Two   & Second row text \\
-Three   & Third row text \\
-      & Fourth row text \\
-\bottomrule
-\end{tabular}
-\end{center}
-\end{table}
-
-\subsection{Wide tables}
-
-Table~\ref{tab:wide-table} is an example of a wide table that spreads across both columns.
-The same can be done for wide figures that should spread across the whole width of the page.
-
-\begin{table*}
-\caption{Wide-table caption}
-\label{tab:wide-table}
-\begin{center}
-\begin{tabular}{llr}
-\toprule
-Heading1 & Heading2 & Heading3\\
-\midrule
-A & A very long text, longer that the width of a single column & $128$\\
-B & A very long text, longer that the width of a single column & $3123$\\
-C & A very long text, longer that the width of a single column & $-32$\\
-\bottomrule
-\end{tabular}
-\end{center}
-\end{table*}
-
-\section{Math expressions and formulas}
-
-Math expressions and formulas that appear within the sentence should be written inside the so-called \emph{inline} math environment: $2+3$, $\sqrt{16}$, $h(x)=\mathbf{1}(\theta_1 x_1 + \theta_0>0)$.
-Larger expressions and formulas (e.g., equations) should be written in the so-called \emph{displayed} math environment:
-
-\[
-b^{(i)}_k = \begin{cases}
-1 & \text{if 
-    $k = \text{argmin}_j \| \mathbf{x}^{(i)} - \mathbf{\mu}_j \|,$}\\
-0 & \text{otherwise}
-\end{cases}
-\]
-
-Math expressions which you reference in the text should be written inside the \textit{equation} environment:
-
-\begin{equation}\label{eq:kmeans-error}
-J = \sum_{i=1}^N \sum_{k=1}^K 
-b^{(i)}_k \| \mathbf{x}^{(i)} - \mathbf{\mu}_k \|^2
-\end{equation}
-
-Now you can reference equation \eqref{eq:kmeans-error}.
-If the paragraph continues right after the formula
-
-\begin{equation}
-f(x) = x^2 + \varepsilon
-\end{equation}
-
-\noindent like this one does, use the command \emph{noindent} after the equation to remove the indentation of the row.
-
-Multi-letter words in the math environment should be written inside the command \emph{mathit}, otherwise \LaTeX{} will insert spacing between the letters to denote the multiplication of values denoted by symbols.
-For example, compare
-$\mathit{Consistent}(h,\mathcal{D})$ and\\
-$Consistent(h,\mathcal{D})$.
-
-If you need a math symbol, but you don't know the corresponding \LaTeX{} command that generates it, try
-\emph{Detexify}.\footnote{\texttt{http://detexify.kirelabs.org/}}
-
-\section{Referencing literature}
-
-References to other publications should be written in brackets with the last name of the first author and the year of publication, e.g., \citep{chomsky-73}.
-Multiple references are written in sequence, one after another, separated by semicolon and without whitespaces in between, e.g., \citep{chomsky-73,chave-64,feigl-58}.
-References are typically written at the end of the sentence and necessarily before the sentence punctuation.
-
-If the publication is authored by more than one author, only the name of the first author is written, after which abbreviation \emph{et al.}, meaning \emph{et alia}, i.e.,~and others is written as in \citep{johnson-etc}.
-If the publication is authored by only two authors, then the last names of both authors are written \citep{johnson-howells}.
-
-If the name of the author is incorporated into the text of the sentence, it should not be in the brackets (only the year should be there).
-E.g.,~``\citet{chomsky-73} suggested that \dots''.
-The difference is whether you reference the publication or the author who wrote it.
-
-The list of all literature references is given alphabetically at the end of the paper.
-The form of the reference depends on the type of the bibliographic unit: conference papers~\citep{chave-64}, books~\citep{butcher-81}, journal articles~\citep{howells-51}, doctoral dissertations~\citep{croft-78}, and book chapters~\citep{feigl-58}.
-
-All of this is automatically produced when using BibTeX. Insert all the BibTeX entries into the file \texttt{tar2023.bib}, and then reference them via their symbolic names.
+Finally, a section which describes the acquired results.
 
@@
 It should not exceed half of a column and is typically split into 2--3 paragraphs.
-No new information should be presented in the conclusion;
-this section only summarizes and concludes the paper.
+No new information should be presented in the conclusion; this section only summarizes and concludes the paper.
 
@@
 
-If suitable, you can include the \textit{Acknowledgements} section before inserting the literature references  in order to thank those who helped you in any way to deliver the paper, but are not co-authors of the paper.
+Here we can write a thank you to the professors and the assistants which were involved in TAR class.
 

### 2023-06-03 paper/paper.tex
Paper update - finished model description

@@
 \usepackage{amssymb}
+\usepackage{cleveref}
 
@@
 
-In scientific papers, this section usually (but not necessarily) briefly describes the related research and what makes the presented approach different from it.
+In scientific papers, this section usually ( but not necessarily ) briefly describes the related research and what makes the presented approach different from it.
 Demonstration of citing~\citep{maguire-76}.
@@
 
-\section{Baseline Models}
+\section{Models}
+Motivated by the results of the before mentioned paper, our approach focused on three different models which solve the given classification problem.
+\hfill \break
+\hfill \break
+Firstly we will introduce the \textbf{logistic regression} model which the authors of the dataset presented as the best solution, excluding state-of-the-art solutions such as BERT.
+Then we are going to introduce two transformer approaches, one being \textbf{DistilBERT} and the other one, currently very popular, \textbf{Chat GPT 3.5 Turbo}.
 
-This section which will describe the models that were used to determine the
+\subsection{Preprocessing}
+Before we trained our models we needed to do some form of preprocessing on our data.
+This step is important because it enables adequate learning from the training set.
+Given the dataset already contained pretty clean and structured data, we didn't need to do a lot of preprocessing to get the desired results.
+We started with the basic stop word removal, followed by digit and punctuation removal.
+Then we performed lemmatization which enabled us to properly train the word embeddings for the logistic regression model and tokenizer for the DistilBERT model.
+
+\subsection{Logistic regression}
+Logistic regression is a commonly used machine learning model which can be used for binary classification problem.
+This is a simple model which doesn't require long and expensive training, so, inspired by the great results that this model showed in the original paper (F-score of 79.8 ~\citep{turcan-mckeown-2019-dreaddit}), we have also decided to
+include it in our own research.
+\hfill \break
+\hfill \break
+Logistic regression model expects a fixed size input but words and sentences in natural language can be of any size.
+Today this problem is solved by using word embeddings which represent words from our dataset as multidimensional vectors.
+Their advantage over some other approaches that were used in the past, such as one-hot vector representation, is that they are able to find relations between words and produce similar vectors for similar words.In our approach we used \textbf{word2Vec}~\citep{mikolov2013efficient} embeddings which were trained on the whole training dataset and produced 300-dimensional representations.
+Learned word embeddings were then used for calculating the final representation for each training example.
+Here we experimented with 2 approaches:
+\begin{enumerate}
+    \item \label{itm:one} \textbf{Averaging of word embeddings:} summing up each representation in the input sequence and dividing it with the number of words in the sequence
+    \item \textbf{TF-IDF averaging:} Term Frequency - Inverse Document Frequency is an algorithm that is used to determine an importance of the given word in the document.
+    Importance is represented as a scalar value.
+     This scalar value for each word is then multiplied with the word's corresponding representation.
+    The final representation is then calculated in the same way as described in~\ref{itm:one}.
+
+\end{enumerate}
+
+\subsection{DistilBERT}
+The second model we used was DistilBERT~\citep{sanh2020distilbert}.
+This model comes from the family of deep learning models called transformers~\citep{vaswani2017attention}.
+The main advantage of these types of models is the self-attention mechanism.
+Self-attention allows the model to find the importance of each word in a sequence and build more effective contextual representations.
+\hfill \break
+\hfill \break
+DistilBERT is a model similar to the more popular BERT~\citep{devlin2019bert}, but faster and more lightweight while still preserving almost all the capabilities of the larger model.
+Because of its features and our limited hardware we decided it would be the best option for representing current SOTA solution in the field of transformers.
+Model and tokenizer were trained simultaneously on the whole training set using the implementations from the \textit{HuggingFace} library.
+
+\subsection{Chat GPT 3.5 Turbo}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\textwidth]{images/chat-gpt-prompt}
+    \caption{Text input for Chat GPT 3.5 Turbo API}
+    \label{fig:chat-gpt-prompt}
+\end{figure}
+
+The final model that we used in our research was Chat GPT 3.5 Turbo.
+This model was developed by OpenAI and it aims to generate human like responses based on the provided input text.
+We couldn't perform direct training on this model, but instead we used the provided API to prompt the model to give us the classification result for each example in the test set.
+You can see how we formulated our prompt in figure~\ref{fig:chat-gpt-prompt}.
+
+Given results were then cleaned up
 

### 2023-06-03 paper/paper.tex
Add dataset section

--- 2023-05-31 paper/paper.tex
@@
 \usepackage{amssymb}
+\usepackage{multirow}
 
@@
 In scientific papers, this section usually (but not necessarily) briefly describes the related research and what makes the presented approach different from it.
-Demonstration of citing~\citep{maguire-76}.
 
@@
 
-A section that will be used to describe the dataset that was used in the research paper.
+The dataset that is used in this paper was introduced in a paper which collected posts from a social media webside called Reddit~\citep{dreaddit}.
+On that website users can create posts in communities which focus on specific topics called subreddits.
+
+The dataset consists of posts from subreddits where stressful topics are likely to be discussed in between January 1, 2017 and November 19, 2018.
+These subreddits fall into one of these categories:
+
+\begin{itemize}
+    \item \textbf{Social}: The posts from this category are from the subreddit called \verb|r/relationships|.
+        Posts from this subreddit talk about problems in a relationships, romantic or non-romantic.
+    \item \textbf{Abuse}: posts from this category describe topics related to abuse in relationships and users share their experiences and advices.
+        Subreddits that fall into this category are \verb|r/domesticviolence| and \verb|r/survivorofabuse|.
+    \item \textbf{Anxiety}: subreddits from this category are \verb|r/anxiety| and \verb|r/stress|.
+        Users in posts from this category talk about these mental illnesses, their symptoms, share advices and stories regarding these illnesses.
+    \item \textbf{PTSD}: Same as the Anxiety category, posts from this category talk about mental illness, but focus on Post-Traumatic Stress Disorder.
+        The only subreddit from this category is \verb|r/ptsd| and same as with posts from the Anxiety category, users share advices and stories and ask questions about the illness.
+    \item \textbf{Financial}: posts from subreddits that fall into this category talk about difficult financial situations, share stories about homelessness and other stressful financial topics.
+        Subreddits from this category are \verb|r/almosthomeless|, \verb|r/assistance|, \verb|r/food_pantry| and \verb|r/homeless|.
+\end{itemize}
+
+In the dataset there are in total 187,444 posts from these 10 subreddits.
+The distribution of these posts can be seen in the Table~\ref{tab:dataset-distribution}.
+
+\begin{table*}
+    \caption{Distribution of collected posts}
+    \label{tab:dataset-distribution}
+    \begin{center}
+        \begin{tabular}{|l|l|r|r|r|}
+            \hline
+            \textbf{Topic} & \textbf{Subreddit Name} & \textbf{Total Posts} & \textbf{Avg Tokens/Post} & \textbf{Labeled Segments}\\
+            \hline
+            Social                     & r/relationships    & 107,908 & 578 & 694 \\ \hline
+            \multirow{2}{*}{Abuse}     & r/domesticviolence & 1,529   & 365 & 388 \\
+                                       & r/survivorsofabuse & 1,372   & 444 & 315 \\ \hline
+            \multirow{2}{*}{Anxiety}   & r/anxiety          & 58,130  & 193 & 650 \\
+                                       & r/stress           & 1,078   & 107 & 78  \\ \hline
+            PTSD                       & r/ptsd             & 4,910   & 265 & 711 \\ \hline
+            \multirow{4}{*}{Financial} & r/almosthomeless   & 547     & 261 & 99  \\
+                                       & r/assistance       & 9,243   & 209 & 355 \\
+                                       & r/food\_pantry     & 343     & 187 & 43  \\
+                                       & r/homeless         & 2,384   & 143 & 220 \\ \hline
+        \end{tabular}
+    \end{center}
+\end{table*}
+
+\subsection{Data Annotation}
+
+A portion of the data was annotated using Amazon Mechanical Turk, a crowdsourcing marketplace that allows individuals to outsource jobs.
+
+Primary job for annotators was to determine if there was stress present in the sentence that they were presented.
+The definition for stress was taken from the Oxford English Dictionary states that stress is `a state of mental or emotional strain or tension resulting from adverse or demanding circumstance'.
+Each annotator first had to take a qualification test to ensure that they would label the sentences correctly.
+In the qualification test annotators were given instructions on how to correctly label post segments.
+
+After that, each annotator was given 5 segments which they had to annotate with one of the following labels: ``Stress'', ``Not Stress'' or ``Can't Tell''.
+In addition to the qualification test, each annotator was given one of the 50 `check questions' which were labeled by creators of the dataset.
+If they did not label these `check questions' correctly their annotations were not included in the final dataset.
+
+Since posts can often be longer, which would prove to be complicated for the annotators to label, they were divided into five-sentence chunks.
+Added bonus of this technique is that the data can be used to determine the specific location of stress in the post.
+
+In total, 3,553 labeled data points were collected out of which 39\% had perfect agreement.
+With 52.3\% of the data being labeled as stressful, the dataset is nearly perfectly balanced.
+Labeled data was split into two subsets: train and test subset.
+The train subset contains 2,838 data points and the test subset consists of 715 data points.
 

### 2023-06-03 paper/upute.tex
Add dataset section

% Paper template for TAR 2022
% (C) 2014 Jan Šnajder, Goran Glavaš, Domagoj Alagić, Mladen Karan
% TakeLab, FER

\documentclass[10pt, a4paper]{article}

\usepackage{tar2023}

\usepackage[utf8]{inputenc}
\usepackage[pdftex]{graphicx}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{amssymb}

\title{TAR System Description Paper Template}

\name{Author1, Author2, Author3}

\address{
University of Zagreb, Faculty of Electrical Engineering and Computing\\
Unska 3, 10000 Zagreb, Croatia\\ 
\texttt{autor1@xxx.hr}, \texttt{\{autor2,autor3\}@zz.com}\\
}

\abstract{ 
This document provides the instructions on formatting the TAR system description paper in \LaTeX{}. This is where you write the abstract (i.e., summary) of the work you carried out within the project. The abstract is a paragraph of text ranging between 70 and 150 words.
}

\begin{document}

\maketitleabstract

\section{Introduction}

This section is the introduction to your paper.
Introduction should not be too elaborate, as that is what other sections are for (the Introduction should definitely not spill over to the second page).

This is the second paragraph of the introduction.
In \LaTeX , paragraphs are separated by inserting an empty line in between them.
Avoid very large paragraphs (larger than half of the page height), but also avoid tiny paragraphs (e.g., one-sentence paragraphs)

\section{Second section}

In scientific papers, this section usually (but not necessarily) briefly describes the related research and what makes the presented approach different from it.

\subsection{First subsection}
\label{sec:first}

This is a subsection of the second section.

\subsection{Second subsection}

This is the second subsection of the second section.
Referencing the (sub)sections in text is performed as follows: ``in Section~\ref{sec:first} we have shown \dots''.

\subsubsection{Sub-subsection example}

This is a sub-subsection.
If possible, it is better to avoid sub-subsections.

\section{Extent of the paper}

The paper should have a minimum of 3 and a maximum of 4 pages, plus an additional page for references.

\section{Figures and tables}

\subsection{Figures}

Here is an example on how to include figures in the paper.
Figures are included in \LaTeX{} code immediately \textit{after} the text in which these figures are referenced.
Allow \LaTeX{} to place the figure where it believes is best (usually on top of the page of at the position where you would not place the figure).
Figures are referenced as follows: ``Figure~\ref{fig:figure1} shows \dots''.
Use tilde (\verb.~.) to prevent separation between the word ``Figure'' and its enumeration.

\begin{figure}
\begin{center}
    \includegraphics[width=\columnwidth]{}
\caption{This is the figure caption. Full sentences should be followed with a dot. The caption should be placed \textit{below} the figure. Caption should be short; details should be explained in the text.}
\label{fig:figure1}
\end{center}
\end{figure}

\subsection{Tables}

There are two types of tables: narrow tables that fit into one column and a wide table that spreads over both columns.

\subsubsection{Narrow tables}

Table~\ref{tab:narrow-table} is an example of a narrow table.
Do not use vertical lines in tables -- vertical tables have no effect and they make tables visually less attractive.
We recommend using \textit{booktabs} package for nicer tables.

\begin{table}
\caption{This is the caption of the table. Table captions should be placed \textit{above} the table.}
\label{tab:narrow-table}
\begin{center}
\begin{tabular}{ll}
\toprule
Heading1 & Heading2 \\
\midrule
One & First row text \\
Two   & Second row text \\
Three   & Third row text \\
      & Fourth row text \\
\bottomrule
\end{tabular}
\end{center}
\end{table}

\subsection{Wide tables}

Table~\ref{tab:wide-table} is an example of a wide table that spreads across both columns.
The same can be done for wide figures that should spread across the whole width of the page.

\begin{table*}
\caption{Wide-table caption}
\label{tab:wide-table}
\begin{center}
\begin{tabular}{llr}
\toprule
Heading1 & Heading2 & Heading3\\
\midrule
A & A very long text, longer that the width of a single column & $128$\\
B & A very long text, longer that the width of a single column & $3123$\\
C & A very long text, longer that the width of a single column & $-32$\\
\bottomrule
\end{tabular}
\end{center}
\end{table*}

\section{Math expressions and formulas}

Math expressions and formulas that appear within the sentence should be written inside the so-called \emph{inline} math environment: $2+3$, $\sqrt{16}$, $h(x)=\mathbf{1}(\theta_1 x_1 + \theta_0>0)$.
Larger expressions and formulas (e.g., equations) should be written in the so-called \emph{displayed} math environment:

\[
b^{(i)}_k = \begin{cases}
1 & \text{if 
    $k = \text{argmin}_j \| \mathbf{x}^{(i)} - \mathbf{\mu}_j \|,$}\\
0 & \text{otherwise}
\end{cases}
\]

Math expressions which you reference in the text should be written inside the \textit{equation} environment:

\begin{equation}\label{eq:kmeans-error}
J = \sum_{i=1}^N \sum_{k=1}^K 
b^{(i)}_k \| \mathbf{x}^{(i)} - \mathbf{\mu}_k \|^2
\end{equation}

Now you can reference equation \eqref{eq:kmeans-error}.
If the paragraph continues right after the formula

\begin{equation}
f(x) = x^2 + \varepsilon
\end{equation}

\noindent like this one does, use the command \emph{noindent} after the equation to remove the indentation of the row.

Multi-letter words in the math environment should be written inside the command \emph{mathit}, otherwise \LaTeX{} will insert spacing between the letters to denote the multiplication of values denoted by symbols.
For example, compare
$\mathit{Consistent}(h,\mathcal{D})$ and\\
$Consistent(h,\mathcal{D})$.

If you need a math symbol, but you don't know the corresponding \LaTeX{} command that generates it, try
\emph{Detexify}.\footnote{\texttt{http://detexify.kirelabs.org/}}

\section{Referencing literature}

References to other publications should be written in brackets with the last name of the first author and the year of publication, e.g., \citep{chomsky-73}.
Multiple references are written in sequence, one after another, separated by semicolon and without whitespaces in between, e.g., \citep{chomsky-73,chave-64,feigl-58}.
References are typically written at the end of the sentence and necessarily before the sentence punctuation.

If the publication is authored by more than one author, only the name of the first author is written, after which abbreviation \emph{et al.}, meaning \emph{et alia}, i.e.,~and others is written as in \citep{johnson-etc}.
If the publication is authored by only two authors, then the last names of both authors are written \citep{johnson-howells}.

If the name of the author is incorporated into the text of the sentence, it should not be in the brackets (only the year should be there).
E.g.,~``\citet{chomsky-73} suggested that \dots''.
The difference is whether you reference the publication or the author who wrote it.

The list of all literature references is given alphabetically at the end of the paper.
The form of the reference depends on the type of the bibliographic unit: conference papers~\citep{chave-64}, books~\citep{butcher-81}, journal articles~\citep{howells-51}, doctoral dissertations~\citep{croft-78}, and book chapters~\citep{feigl-58}.

All of this is automatically produced when using BibTeX. Insert all the BibTeX entries into the file \texttt{tar2023.bib}, and then reference them via their symbolic names.

\section{Conclusion}

Conclusion is the last enumerated section of the paper.
It should not exceed half of a column and is typically split into 2--3 paragraphs.
No new information should be presented in the conclusion;
this section only summarizes and concludes the paper.

\section*{Acknowledgements}

If suitable, you can include the \textit{Acknowledgements} section before inserting the literature references  in order to thank those who helped you in any way to deliver the paper, but are not co-authors of the paper.

\bibliographystyle{tar2023}
\bibliography{tar2023}

\end{document}

### 2023-06-03 paper/paper.tex

@@
 \usepackage{multirow}
+\usepackage{cleveref}
 

### 2023-06-03 paper/paper.tex
Fix conflicts

@@
 
-The dataset that is used in this paper was introduced in a paper which collected posts from a social media webside called Reddit~\citep{dreaddit}.
+The dataset that is used in this paper was introduced in a paper which collected posts from a social media webside called Reddit~\citep{turcan-mckeown-2019-dreaddit}.
 On that website users can create posts in communities which focus on specific topics called subreddits.

### 2023-06-04 paper/paper.tex
Close to finishing paper

@@
 \usepackage{cleveref}
+\usepackage{biblatex}
+\addbibresource{}
 
-\title{Stress Analysis in Social Media}
+\title{Transformers, do we really need them for detecting stress?}
 
@@
 
-This section is the introduction to your paper.
+Stress is a very common feeling everyone experiences in a smaller or larger amount during their life.
+It negatively impacts our health and detecting it could enable us to help the person who is experiencing it and improve their existing situation.
+This paper will try to find the optimal approach of detecting stressful situations from user descriptions.
+For this task we will be using the Dreaddit dataset which contains user posts from the Reddit website.
+Throughout this paper we will be referencing the original one where the dataset was introduced.
+\hfill \break
+\hfill \break
+In the first part of the paper we are going to describe the dataset, followed by the models that we decided to use to tackle the problem.
+We tried to continue the research of the authors of the dataset and use their best performing model to compare it with some other currently popular solutions.
+In the end we are going to try to answer the question if the more complex and costly solutions were really justified or should this problem be solved with a more simple approach.
 
 \section{Related Work}
+Stress detection was researched in a couple of other approaches in the last couple of years.
+One of the approaches was detecting stress using deep neural networks and psychological signals~\citep{stress-neural}.
 
-In scientific papers, this section usually (but not necessarily) briefly describes the related research and what makes the presented approach different from it.
+The approach that we looked at the most was by the authors of the dataset\
 
@@
 \section{Models}
-Motivated by the results of the before mentioned paper, our approach focused on three different models which solve the given classification problem.
+Motivated by the results of the aforementioned paper, our approach focused on three different models which solve the given classification problem.
 \hfill \break
 \hfill \break
-Firstly we will introduce the \textbf{logistic regression} model which the authors of the dataset presented as the best solution, excluding state-of-the-art solutions such as BERT.
+Firstly we will introduce the \textbf{logistic regression} model which the authors of the dataset presented as the best solution, excluding state-of-the-art (SOTA) solutions such as BERT.
+This model is going to represent a simple model approach to the problem without using more complex solutions such as transformers.
 Then we are going to introduce two transformer approaches, one being \textbf{DistilBERT} and the other one, currently very popular, \textbf{Chat GPT 3.5 Turbo}.
+
+We performed our training on the whole dataset and our focus wasn't to get the best possible results for each model but to compare them and find out which is best suited for the given classification task (taking into account the cost of the model).
+Because of that reason we also didn't remove lower agreement rate examples from our training dataset to see how our models deal with learning harder examples.
 
@@
 \subsection{Logistic regression}
-Logistic regression is a commonly used machine learning model which can be used for binary classification problem.
+Logistic regression~\citep{logreg} is a commonly used machine learning model which can be used for binary classification problem.
 This is a simple model which doesn't require long and expensive training, so, inspired by the great results that this model showed in the original paper (F-score of 79.8 ~\citep{turcan-mckeown-2019-dreaddit}), we have also decided to
@@
 
-\subsection{Chat GPT 3.5 Turbo}
-
 \begin{figure}
@@
 
+\subsection{Chat GPT 3.5 Turbo}
 The final model that we used in our research was Chat GPT 3.5 Turbo.
@@
 
-Given results were then cleaned up
+It must be mentioned that there was some manual data cleanup needed after we got the responses from the API (labels contained an explanation behind the given result)
+
+\begin{table*}
+    \centering
+    \caption{Different model results}
+    \label{tab:model-results}
+    \begin{center}
+        \begin{tabular}{|l|c|c|c|}
+            \hline
+            \textbf{Model} & \textbf{P} & \textbf{R} & \textbf{F1} \\ \hline
+            LR + averaged word2Vec embeddings & 0.6441 & 0.7995 & 0.7134 \\ \hline
+            LR + TF-IDF averaged word2Vec embeddings & 0.6859 & 0.8049 & \textbf{0.7406} \\ \hline
+            DistilBERT & 0.7105 & 0.7913 & 0.7487 \\ \hline
+            Chat GPT 3.5 Turbo & 0.6905 & \textbf{0.9431} & 0.7972 \\ \hline
+        \end{tabular}
+    \end{center}
+\end{table*}
 
@@
 
-Finally, a section which describes the acquired results.
+The results of our four different models are present in table~\ref{tab:model-results}.
+We can see that our logistic regression (LR) model with basic word embedding averaging performed the worst, what was expected given its simplicity.
+This simple model, however, performs much better when we introduce TF-IDF averaging.
+\subsection{LR(TF-IDF averaging) vs DistilBERT}
+LR model with TF-IDF averaging performed very similarly to the DistilBERT approach.
+Transformers are currently SOTA approach in NLP and we expect them to perform much better than the simpler models.
+However, classifying stress, using this pretty clean dataset, isn't a particularly hard task and our logistic regression model deals very well with the problem, which is also what authors of the original dataset pointed out.
+\hfill \break
+\hfill \break
+Here we compared only the results of the two models not taking into account the cost of the more complex model.
+Training of the DistilBERT model took longer and required more hardware just to get worse results.
+This leads us to the conclusion that sometimes the solution to the problem could be a simple model without the need for more complex and expensive solutions.
+\\
 
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\textwidth]{images/conf-matrix-chatgpt}
+    \caption{Confusion matrix for Chat GPT 3.5 Turbo. 0 represents data labeled not stressed while 1 represents data labeled stressed.}
+    \label{fig:chat-gpt-conf-matrix}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\textwidth]{images/conf-matrix-logreg}
+    \caption{Confusion matrix for LR with TF-IDF averaging.}
+    \label{fig:logreg-conf-matrix}
+\end{figure}
+
+\subsection{DistilBERT vs Chat GPT}
+In our two transformer approaches Chat GPT showed much better results.
+What shows the true power of this transformer model is that, even though it wasn't strictly trained on the training data, it managed to outperform DistilBERT model.
+As we can see in figure ~\ref{fig:chat-gpt-conf-matrix} this model managed to have an extremely low number of false negative (FN) predictions.
+In certain cases we would want to prefer this behaviour where we want to detect stress and help the person who is experiencing it.
+
+The downside of this approach is the cost behind it.
+Chat GPT API is a paid service and if we want to use this approach in for stress detection this might not be the best option if our budget is limited.
+
+\subsection{LR (TF-IDF) vs Chat GPT}
+We can see that Chat GPT performed better than our LR model when we compare their F1 scores.
+The change comes primarily from the higher recall score which Chat GPT manages to achieve (less false negative examples).
+While we can look at the scores by themselves and conclude that Chat GPT is a better model for the given task, this approach doesn't take into account the cost of the model.
+
+Our simpler LR model achieves comparable results to the SOTA solution and we claim that it is the optimal approach for solving stress classification problem from the given dataset.
+Model is easy to learn and could even get better results if it was trained on the dataset which contained examples with higher agreement factor, as it was shown from the authors of the dataset.
 \section{Conclusion}
-
-Conclusion is the last enumerated section of the paper.
-It should not exceed half of a column and is typically split into 2--3 paragraphs.
-No new information should be presented in the conclusion; this section only summarizes and concludes the paper.
 

### 2023-06-04 paper/paper.tex
Removed errors
Finished paper

@@
 \usepackage{cleveref}
-\usepackage{biblatex}
-\addbibresource{}
+\usepackage{float}
 
@@
 One of the approaches was detecting stress using deep neural networks and psychological signals~\citep{stress-neural}.
-
-The approach that we looked at the most was by the authors of the dataset\
+This work however focused more on the medical aspects of stress while our aim was to detect stress using persons description of an event.
+The approach that we looked at the most was by the authors of the dataset~\citep{turcan-mckeown-2019-dreaddit}.
+They focused on developing the dataset as well as testing how different models solved the given task.
 
@@
 Then we are going to introduce two transformer approaches, one being \textbf{DistilBERT} and the other one, currently very popular, \textbf{Chat GPT 3.5 Turbo}.
-
+\hfill \break
+\hfill \break
 We performed our training on the whole dataset and our focus wasn't to get the best possible results for each model but to compare them and find out which is best suited for the given classification task (taking into account the cost of the model).
-Because of that reason we also didn't remove lower agreement rate examples from our training dataset to see how our models deal with learning harder examples.
+Because of that reason, we also didn't remove lower agreement rate examples from our training dataset to enable our models to handle even the harder examples which are inevitable in the real applications.
 
@@
 include it in our own research.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.5\textwidth]{images/embeddings}
+    \caption{Relations between similar word vectors}
+    \label{fig:embedding}
+\end{figure}
 \hfill \break
 \hfill \break
-Logistic regression model expects a fixed size input but words and sentences in natural language can be of any size.
-Today this problem is solved by using word embeddings which represent words from our dataset as multidimensional vectors.
-Their advantage over some other approaches that were used in the past, such as one-hot vector representation, is that they are able to find relations between words and produce similar vectors for similar words.In our approach we used \textbf{word2Vec}~\citep{mikolov2013efficient} embeddings which were trained on the whole training dataset and produced 300-dimensional representations.
+\hfill \break
+Logistic regression expects a fixed size input but words and sentences in natural language can be of any size.
+Today, this problem is solved by using word embeddings which represent words from our dataset as multidimensional vectors.
+Their advantage over some other approaches that were used in the past, such as one-hot vector representation, is that they are able to find relations between words and produce similar vectors for similar words.
+The relation between similar words can be seen in figure~\ref{fig:embedding}.
+In our approach we used \textbf{word2Vec}~\citep{mikolov2013efficient} embeddings which were trained on the whole training dataset and produced 300-dimensional representations.
 Learned word embeddings were then used for calculating the final representation for each training example.
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.5\textwidth]{images/chat-gpt-prompt}
-    \caption{Text input for Chat GPT 3.5 Turbo API}
-    \label{fig:chat-gpt-prompt}
-\end{figure}
-
 \subsection{Chat GPT 3.5 Turbo}
@@
 It must be mentioned that there was some manual data cleanup needed after we got the responses from the API (labels contained an explanation behind the given result)
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\textwidth]{images/chat-gpt-prompt}
+    \caption{Text input for Chat GPT 3.5 Turbo API}
+    \label{fig:chat-gpt-prompt}
+\end{figure}
 
@@
 Here we compared only the results of the two models not taking into account the cost of the more complex model.
-Training of the DistilBERT model took longer and required more hardware just to get worse results.
+Training of the DistilBERT model took longer and required more hardware just to get similar results.
 This leads us to the conclusion that sometimes the solution to the problem could be a simple model without the need for more complex and expensive solutions.
@@
 What shows the true power of this transformer model is that, even though it wasn't strictly trained on the training data, it managed to outperform DistilBERT model.
-As we can see in figure ~\ref{fig:chat-gpt-conf-matrix} this model managed to have an extremely low number of false negative (FN) predictions.
-In certain cases we would want to prefer this behaviour where we want to detect stress and help the person who is experiencing it.
+As we can see in figure~\ref{fig:chat-gpt-conf-matrix} this model managed to have an extremely low number of false negative (FN) predictions.
+In certain cases we would want to prefer this behaviour where not detecting stress represents a big problem.
 
@@
 Model is easy to learn and could even get better results if it was trained on the dataset which contained examples with higher agreement factor, as it was shown from the authors of the dataset.
+
+If we have more resources and a bigger budget, Chat GPT with its powerful API service could be a better choice, mainly because it rarely doesn't detect stress which could definitely help in certain situations.
 \section{Conclusion}
 
-\section*{Acknowledgements}
-
-Here we can write a thank you to the professors and the assistants which were involved in TAR class.
+In this paper we looked at different approaches for detecting stress from the Dreaddit dataset.
+We continued our research on findings of the authors and tried to find out if more complex models and solutions gave much better results.
+\hfill \break
+\hfill \break
+We believe that the simple model solves this problem well enough and that more complex and expensive transformer solutions aren't worth the extra cost.
+In some rare cases, where not detecting stress could pose a problem, we can suggest trying the Chat GPT API service if the demand isn't high and the budget isn't very limited.
 

### 2023-06-04 paper/paper.tex
Cleanup and add abstract

@@
 \abstract{
-    Here we can write an abstract of the paper.
-    The abstract is a paragraph of text ranging between 70 and 150 words.
+    Sentiment analysis is a prominent branch of machine learning and, more specifically, natural language processing that is advancing from day to day.
+    In the modern day and age where negative emotions such as stress are present in everyday life of most people social media allows them to share those emotions with the world at every moment.
+    Using those posts from social media the dataset Dreaddit was created which collected posts from a social media site called Reddit with the purpose of detecting stress in those posts.
+    In this paper we will explore different deep learning models to find which approach is most effective in detecing stress from text.
+    Some models that we worked with were logistic regression along with two transformer approaches: DistilBERT and Chat GPT 3.5 Turbo.
 }
@@
 On that website users can create posts in communities which focus on specific topics called subreddits.
-
+\hfill \break
+\hfill \break
 The dataset consists of posts from subreddits where stressful topics are likely to be discussed in between January 1, 2017 and November 19, 2018.
@@
 A portion of the data was annotated using Amazon Mechanical Turk, a crowdsourcing marketplace that allows individuals to outsource jobs.
-
+\hfill \break
+\hfill \break
 Primary job for annotators was to determine if there was stress present in the sentence that they were presented.
@@
 In the qualification test annotators were given instructions on how to correctly label post segments.
-
 After that, each annotator was given 5 segments which they had to annotate with one of the following labels: ``Stress'', ``Not Stress'' or ``Can't Tell''.
@@
 If they did not label these `check questions' correctly their annotations were not included in the final dataset.
-
 Since posts can often be longer, which would prove to be complicated for the annotators to label, they were divided into five-sentence chunks.
 Added bonus of this technique is that the data can be used to determine the specific location of stress in the post.
-
+\hfill \break
+\hfill \break
 In total, 3,553 labeled data points were collected out of which 39\% had perfect agreement.
@@
      This scalar value for each word is then multiplied with the word's corresponding representation.
-    The final representation is then calculated in the same way as described in~\ref{itm:one}.
+    The final representation is then calculated in the same way as described in approach~\ref{itm:one}.
 
@@
 
-It must be mentioned that there was some manual data cleanup needed after we got the responses from the API (labels contained an explanation behind the given result)
+It must be mentioned that there was some manual data cleanup needed after we got the responses from the API, such as explanations behind the given results that were contained in the labels.
 
@@
             LR + averaged word2Vec embeddings & 0.6441 & 0.7995 & 0.7134 \\ \hline
-            LR + TF-IDF averaged word2Vec embeddings & 0.6859 & 0.8049 & \textbf{0.7406} \\ \hline
-            DistilBERT & 0.7105 & 0.7913 & 0.7487 \\ \hline
-            Chat GPT 3.5 Turbo & 0.6905 & \textbf{0.9431} & 0.7972 \\ \hline
+            LR + TF-IDF averaged word2Vec embeddings & 0.6859 & 0.8049 & 0.7406 \\ \hline
+            DistilBERT & \textbf{0.7105} & 0.7913 & 0.7487 \\ \hline
+            Chat GPT 3.5 Turbo & 0.6905 & \textbf{0.9431} & \textbf{0.7972} \\ \hline
         \end{tabular}
@@
 In this paper we looked at different approaches for detecting stress from the Dreaddit dataset.
-We continued our research on findings of the authors and tried to find out if more complex models and solutions gave much better results.
+We continued our research on findings of the authors and tried to find out if more complex models and solutions gave better results.
 \hfill \break
@@
 We believe that the simple model solves this problem well enough and that more complex and expensive transformer solutions aren't worth the extra cost.
-In some rare cases, where not detecting stress could pose a problem, we can suggest trying the Chat GPT API service if the demand isn't high and the budget isn't very limited.
+In some rare cases, where not detecting stress could pose a problem, we can suggest trying the Chat GPT API service if the demand isn't high and the budget isn't limited.
 

### 2023-06-04 paper/paper.tex
Finished paper

@@
 \abstract{
-    Sentiment analysis is a prominent branch of machine learning and, more specifically, natural language processing that is advancing from day to day.
-    In the modern day and age where negative emotions such as stress are present in everyday life of most people social media allows them to share those emotions with the world at every moment.
-    Using those posts from social media the dataset Dreaddit was created which collected posts from a social media site called Reddit with the purpose of detecting stress in those posts.
-    In this paper we will explore different deep learning models to find which approach is most effective in detecing stress from text.
-    Some models that we worked with were logistic regression along with two transformer approaches: DistilBERT and Chat GPT 3.5 Turbo.
+    In the modern day and age, where negative emotions such as stress are present in everyday life of most people, social media allows them to share those emotions with the world.
+    Using posts from the social media site Reddit, the dataset Dreaddit was created.
+    In this paper we will explore different approaches for stress detection using some simple and some more advanced models.
+    Models that we worked with were logistic regression along with two transformer approaches: DistilBERT and Chat GPT 3.5 Turbo.
+    Our goal was to compare these different approaches to stress detection and find out which model would produce the best results while also not being too expensive and complex.
 }
@@
 On that website users can create posts in communities which focus on specific topics called subreddits.
+\hfill \break
 \hfill \break
@@
 
+\hfill \break
+\hfill \break
 \subsection{Data Annotation}
@@
 \end{figure}
-\hfill \break
-\hfill \break
 \hfill \break
@@
 In some rare cases, where not detecting stress could pose a problem, we can suggest trying the Chat GPT API service if the demand isn't high and the budget isn't limited.
+Transformers may be a better option if we just look at their capabilities, but at what cost?
+Sometimes the simpler solution gets the job done and we should stick to it.
 

### 2023-06-29 paper/paper.tex
Fixes

@@
 This paper will try to find the optimal approach of detecting stressful situations from user descriptions.
-For this task we will be using the Dreaddit dataset which contains user posts from the Reddit website.
+For this task we will be using the Dreaddit dataset~\citep{turcan-mckeown-2019-dreaddit} which contains user posts from the Reddit website.
 Throughout this paper we will be referencing the original one where the dataset was introduced.
@@
 
-The dataset that is used in this paper was introduced in a paper which collected posts from a social media webside called Reddit~\citep{turcan-mckeown-2019-dreaddit}.
+The dataset that is used in this paper was introduced in a paper which collected posts from a webside Reddit~\citep{turcan-mckeown-2019-dreaddit}.
 On that website users can create posts in communities which focus on specific topics called subreddits.
@@
     \item \textbf{Social}: The posts from this category are from the subreddit called \verb|r/relationships|.
-        Posts from this subreddit talk about problems in a relationships, romantic or non-romantic.
+        Posts from this subreddit talk about problems in relationships, romantic or non-romantic.
     \item \textbf{Abuse}: posts from this category describe topics related to abuse in relationships and users share their experiences and advices.
@@
 
-In the dataset there are in total 187,444 posts from these 10 subreddits.
+In the dataset there are 187,444 posts in total from these 10 subreddits.
 The distribution of these posts can be seen in the Table~\ref{tab:dataset-distribution}.
@@
 Primary job for annotators was to determine if there was stress present in the sentence that they were presented.
-The definition for stress was taken from the Oxford English Dictionary states that stress is `a state of mental or emotional strain or tension resulting from adverse or demanding circumstance'.
+The definition for stress which was taken from the Oxford English Dictionary states that stress is `a state of mental or emotional strain or tension resulting from adverse or demanding circumstance'.
 Each annotator first had to take a qualification test to ensure that they would label the sentences correctly.
@@
 \hfill \break
-Firstly we will introduce the \textbf{logistic regression} model which the authors of the dataset presented as the best solution, excluding state-of-the-art (SOTA) solutions such as BERT.
+Firstly we will introduce the \textbf{logistic regression}~\citep{logreg} model which the authors of the dataset presented as the best solution, excluding state-of-the-art (SOTA) solutions such as BERT~\citep{devlin2019bert}.
 This model is going to represent a simple model approach to the problem without using more complex solutions such as transformers.
-Then we are going to introduce two transformer approaches, one being \textbf{DistilBERT} and the other one, currently very popular, \textbf{Chat GPT 3.5 Turbo}.
+Then we are going to introduce two transformer approaches, one being \textbf{DistilBERT}~\citep{sanh2020distilbert} and the other one, currently very popular, \textbf{Chat GPT 3.5 Turbo}~\citep{openai2023}.
 \hfill \break
 \hfill \break
-We performed our training on the whole dataset and our focus wasn't to get the best possible results for each model but to compare them and find out which is best suited for the given classification task (taking into account the cost of the model).
-Because of that reason, we also didn't remove lower agreement rate examples from our training dataset to enable our models to handle even the harder examples which are inevitable in the real applications.
+We performed our training on the whole dataset and our focus was not to get the best possible results for each model but to compare them and find out which is best suited for the given classification task (taking into account the cost of the model).
+Because of that reason, we also did not remove lower agreement rate examples from our training dataset to enable our models to handle even the harder examples which are inevitable in the real applications.
 
@@
 This step is important because it enables adequate learning from the training set.
-Given the dataset already contained pretty clean and structured data, we didn't need to do a lot of preprocessing to get the desired results.
+Given the dataset already contained pretty clean and structured data, we did not need to do a lot of preprocessing to get the desired results.
 We started with the basic stop word removal, followed by digit and punctuation removal.
@@
 Logistic regression~\citep{logreg} is a commonly used machine learning model which can be used for binary classification problem.
-This is a simple model which doesn't require long and expensive training, so, inspired by the great results that this model showed in the original paper (F-score of 79.8 ~\citep{turcan-mckeown-2019-dreaddit}), we have also decided to
+This is a simple model which does not require long and expensive training, so, inspired by the great results that this model showed in the original paper (F-score of 79.8 ~\citep{turcan-mckeown-2019-dreaddit}), we have also decided to
 include it in our own research.
@@
 Because of its features and our limited hardware we decided it would be the best option for representing current SOTA solution in the field of transformers.
-Model and tokenizer were trained simultaneously on the whole training set using the implementations from the \textit{HuggingFace} library.
+Model and tokenizer were trained simultaneously on the whole training set using the implementations from the \textit{HuggingFace} library~\citep{wolf2020huggingfaces}.
 
 \subsection{Chat GPT 3.5 Turbo}
-The final model that we used in our research was Chat GPT 3.5 Turbo.
+The final model that we used in our research was Chat GPT 3.5 Turbo~\citep{openai2023}.
 This model was developed by OpenAI and it aims to generate human like responses based on the provided input text.
-We couldn't perform direct training on this model, but instead we used the provided API to prompt the model to give us the classification result for each example in the test set.
+We could not perform direct training on this model, but instead we used the provided API to prompt the model to give us the classification result for each example in the test set.
 You can see how we formulated our prompt in figure~\ref{fig:chat-gpt-prompt}.
@@
 Transformers are currently SOTA approach in NLP and we expect them to perform much better than the simpler models.
-However, classifying stress, using this pretty clean dataset, isn't a particularly hard task and our logistic regression model deals very well with the problem, which is also what authors of the original dataset pointed out.
+However, classifying stress, using this pretty clean dataset, is not a particularly hard task and our logistic regression model deals very well with the problem, which is also what authors of the original dataset pointed out.
 \hfill \break
@@
 In our two transformer approaches Chat GPT showed much better results.
-What shows the true power of this transformer model is that, even though it wasn't strictly trained on the training data, it managed to outperform DistilBERT model.
+What shows the true power of this transformer model is that, even though it was not strictly trained on the training data, it managed to outperform DistilBERT model.
 As we can see in figure~\ref{fig:chat-gpt-conf-matrix} this model managed to have an extremely low number of false negative (FN) predictions.
@@
 The change comes primarily from the higher recall score which Chat GPT manages to achieve (less false negative examples).
-While we can look at the scores by themselves and conclude that Chat GPT is a better model for the given task, this approach doesn't take into account the cost of the model.
+While we can look at the scores by themselves and conclude that Chat GPT is a better model for the given task, this approach does not take into account the cost of the model.
 
@@
 
-If we have more resources and a bigger budget, Chat GPT with its powerful API service could be a better choice, mainly because it rarely doesn't detect stress which could definitely help in certain situations.
+If we have more resources and a bigger budget, Chat GPT with its powerful API service could be a better choice, mainly because it rarely does not detect stress which could definitely help in certain situations.
 \section{Conclusion}
@@
 \hfill \break
-We believe that the simple model solves this problem well enough and that more complex and expensive transformer solutions aren't worth the extra cost.
-In some rare cases, where not detecting stress could pose a problem, we can suggest trying the Chat GPT API service if the demand isn't high and the budget isn't limited.
+We believe that the simple model solves this problem well enough and that more complex and expensive transformer solutions are not worth the extra cost.
+In some rare cases, where not detecting stress could pose a problem, we can suggest trying the Chat GPT API service if the demand is not high and the budget is not limited.
 Transformers may be a better option if we just look at their capabilities, but at what cost?
